opioid_crisis_code

### 2020-05-08 Opioid_Crisis_Code.Rmd
fixed legends

ggplot(data = death_by_year_and_state,
            mapping = aes(x = long, y = lat,
                          fill = `Crude Rate`, group = group)) + 
  geom_polygon(color = "gray90", size = 0.05) + 
  theme_map() +
  scale_fill_gradient(low = "white", high = "#CB454A") +
    guides(fill = guide_legend(nrow = 1)) + 
    theme(legend.position = "bottom")

@@

# map of distribution of treatment centers per capita

ggplot(data = treatment_locations_map_per_cap,
            mapping = aes(x = long, y = lat.y,
                          fill = count_per_pop, group = group)) + 
  geom_polygon(color = "gray90", size = 0.05) + 
  theme_map() +
  scale_fill_gradient(low = "white", high = "#CB454A",
                      breaks = c(0,20,40,60,80,120)) +
    guides(fill = guide_legend(nrow = 1)) + 
    theme(legend.position = "bottom") +
  labs(color = "Number of Treatment Centers in State Per Capita")

>>>>

ggplot(data = death_by_year_and_state,
            mapping = aes(x = long, y = lat,
                          fill = `Crude Rate`, group = group)) + 
  geom_polygon(color = "gray90", size = 0.05) + 
  theme_map() +
  scale_fill_gradient(name = "Overdose Deaths Per Capita/100,000",
                            low = "white", high = "#CB454A",
                            breaks = c(0,5,10,15,20,25,30,35,40,45,50)) +
    guides(fill = guide_legend(nrow = 1)) + 
    theme(legend.position = "bottom")

@@

# map of distribution of treatment centers per capita
treatment_locations_map_per_cap <- treatment_locations_map_per_cap %>%
  rename("Number of Treatment Centers Per Capita" = count_per_pop)

ggplot(data = treatment_locations_map_per_cap,
            mapping = aes(x = long, y = lat.y,
                          fill = `Number of Treatment Centers Per Capita`, group = group)) + 
  geom_polygon(color = "gray90", size = 0.05) + 
  theme_map() +
  scale_fill_gradient(low = "white", high = "#CB454A") +
    guides(fill = guide_legend(nrow = 1)) + 
    theme(legend.position = "bottom") +
  labs(color = "Number of Treatment Centers Per Capita")
